MacLeish: An R package for monitoring environmental conditions in Whately, Massachusetts

### 2022-07-14 joss_paper/paper.Rmd
booktabs

---
title: 'MacLeish: An R package for monitoring environmental conditions in Whately, Massachusetts'
date: "`r Sys.Date()`"
authors:
  - name: Benjamin S. Baumer
    orcid: 0000-0002-3279-0516
    affiliation: 1
  - name: Dominique Kelly
    orcid: 0000-0001-7186-9385
    affiliation: 1
  - name: Albert Y. Kim
    orcid: 0000-0001-7824-306X
    affiliation: 1
affiliations: 
 - name: Smith College, Northampton, Massachusetts, USA  
   index: 1
bibliography: [pkgs.bib, refs.bib]
biblio-style: apa
tags:
  - R
  - forest
  - farmland
  - weather
  - spatial analysis 
output:
  rticles::joss_article:
    keep_md: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: 'MacLeish: An R package for monitoring environmental conditions in Whately, Massachusetts'
date: "`r Sys.Date()`"
authors:
  - name: Benjamin S. Baumer
    orcid: 0000-0002-3279-0516
    affiliation: 1
  - name: Dominique Kelly
    orcid: 0000-0001-7186-9385
    affiliation: 1
  - name: Albert Y. Kim
    orcid: 0000-0001-7824-306X
    affiliation: 1
affiliations: 
 - name: Smith College, Northampton, Massachusetts, USA  
   index: 1
bibliography: [pkgs.bib, refs.bib]
biblio-style: apa
tags:
  - R
  - forest
  - farmland
  - weather
  - spatial analysis 
output:
  rticles::joss_article:
    keep_md: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{booktabs}
---
